---
title: "UT_projections_report"
output: html_document
---

This script runs the testing cost effectiveness transmission functions and outputs results in terms of vaccination rates and testing frequency. 
```{r setup, include=FALSE}
rm(list=ls())
library(ggplot2)
library(deSolve)
library(scales)
library(dplyr)
library(EpiEstim)
library(tidyr)
library(reshape2)
library(cowplot)
library(knitr)
library(forcats)
library(bigsnpr)
library(EnvStats)
library(tidyverse)
library(ggpubr)
library(zoo)
source("testing_cost_effectiveness_fxns.R")
theme_set(theme_cowplot())
ggplot + background_grid(major = "xy", minor = "xy")
PAR_TABLE_PATH<-'../data/par_table.csv'
COST_TABLE_PATH<-'../data/cost_table.csv'
PAR_BOUNDS_PATH<-'../data/par_bounds.csv'
```
Set parameters of model
```{r}
# vaccine and immunity parameters 
e_v = 0.5 
sigma_v = 0.36 # https://www.gov.il/en/departments/news/06072021-04
sym_red = 0.3
psym_v = sym_red/sigma_v

# test parameters
Sp = 0.995 # test specificity
Se = 0.9 # test sensitivity
w_v = 0.5 # proportion of vaccinated population willing to test
w_u = 0.5 # proportion of unvaccinated population willing to test
f_v = 0#1/30 # frequency of testing in vaccinated individuals
f_u =1/7 # frequency of testing in unvaccinated individuals
is = 0.925 # probability of isolating given a positive test 
is_sym = 0.25 # probability of isolating given symptoms
k = 1/2 # rate of confirmation testing
r_r = 1/7 # rate of leaving quarantine asymptomatic or symptomatic quarantine states

# epidemiological parameters
R0 = 5
t_exposed = 3
t_pre_sym = 2.3
t_inf = 7
t_sym_state = t_inf-t_pre_sym
t_quarantine = 7
t_iso = 2 # time to isolate if symptomatic
psym = 0.6
intros_per_week = 5 # something arbitrary for now, lets say 5 infections per week
avg_time_asym = psym*t_pre_sym + (1-psym)*t_inf
avg_time_asym_v= psym_v*t_pre_sym + (1-psym_v)*t_inf
# sanity checks (these don't go into par table)
delta_au = 1/avg_time_asym
delta_av = 1/avg_time_asym_v
delta_s = 1/t_sym_state
delta_q = 1/t_quarantine
beta_a = R0*1/t_inf #transmission rate of asymptomatic individuals
beta_s = R0*1/t_inf # transmission rate of symptomatic individuals 

gamma = 1/3 # rate of transition from exposed to infectious
init_prev = 420/100000 # initial disease prevalence on campus (0.2%) 9x7*3=189 per 100,000
init_rec = 0.40
init_vacc = 0.5
odds_inf_not_vac = 1
init_ru = init_rec- init_rec*init_vacc
init_rv = init_rec*init_vacc
init_sv = (1-init_rec)*init_vacc 
#init_ru = 0.1 # initial recovered unvaccinated
#init_rv = 0.2 # initial vaccinated and previously infected
#init_sv = 0.3 # initial vaccinated susceptible

# scenario parameters
N<- 50000
duration_school_year = 113
tdays<-seq(from = 0, to = duration_school_year, by = 1)
dates<-seq(from = as.Date("2021-08-25"), by = "day", length.out = duration_school_year+1)

# cost parameters
PCR_price = 23
RT_price = 6.25
online_price = 100000
pct_pos_isofac = 2229/3271 # number of student-days in ISOFAC/ number of total positives during that time
isofac_price = 300 #  $100 dollars per student per day
contact_tracing_price = 50 # cost of labor to reach out to each cases contacts
sequencing_price = 60 # need to factor this in
n_rapid_tests_per_kiosk_per_week = 1375#250-300 per site per day *5 = 1250-1500 
price_per_kiosk = 125000 #(50k for 3 kiosks + static SSB site = 50k/4)
DLL_price = 500*15/135#500 per credit * 18 credits per semester/ 135 days per semester
risk_tolerance = 'CDC yellow' 
risk_tolerance = 'CDC orange'

# Uncertainty
R0vals<-c(4.5, 5.5)
init_rec_vals<-c(0.32, 0.48)
psym_vals<-c(0.5, 0.7)
sigma_v_vals<-c(0.25, 0.5) # not sure how to estimate this
sym_red_vals<-c(0.27, 0.35)
is_vals<-c(0.9, 0.95)
is_sym_vals<-c(0.2, 0.33)
intro_vals<-c(4, 6)
init_prev_vals<-c(380/100000, 470/100000)



cost_table<-data.frame(PCR_price, RT_price, online_price, DLL_price, pct_pos_isofac,
                       isofac_price, n_rapid_tests_per_kiosk_per_week, price_per_kiosk,
                       contact_tracing_price, sequencing_price) 

par_table<-data.frame(N, init_prev, init_rec, init_vacc, odds_inf_not_vac, duration_school_year, R0,
                      t_pre_sym,
                      t_inf, t_sym_state, t_quarantine,t_iso,  psym, gamma,psym, e_v, sigma_v,
                      sym_red,intros_per_week,
                      Sp, Se, w_v, w_u, f_v,f_u, is,is_sym, k)
par_bounds<-data.frame(R0vals,init_rec_vals, psym_vals, sigma_v_vals, sym_red_vals, is_sym_vals, is_vals, intro_vals, init_prev_vals)
write.csv(cost_table, '../data/cost_table.csv',row.names = FALSE)
write.csv(par_table,'../data/par_table.csv', row.names = FALSE)
write.csv(par_bounds, '../data/par_bounds.csv', row.names = FALSE)
```

Test to make sure the model with uncertainty runs properly
```{r}
par_table$f_u<-2/7
par_table$init_vacc<-0.7
out_list_uq<-testing_model_w_uncertainty(par_table, cost_table, risk_tolerance, nsamps, par_bounds)
aggr_df_t<-out_list_uq[[4]]
aggr_df<-out_list_uq[[3]]
df_t_sims<-out_list_uq[[2]]

par_table$f_u<-0
par_table$f_v<-0
out_nt_df<-solve_transmission_eqns(par_table)
out_list_uq_nt<-testing_model_w_uncertainty(par_table, cost_table, risk_tolerance, nsamps, par_bounds)
aggr_df_t_nt<-out_list_uq_nt[[4]]
df_t_sims_nt<-out_list_uq_nt[[2]]

Iplot<-ggplot() + geom_line(data = df_t_sims , aes(x = dates, y = I, group = sample), color = "blue", alpha = 0.1) + geom_line(data = aggr_df_t , aes(x = dates, y = I_med), color = "blue")  + geom_line(data = df_t_sims_nt, aes(x = dates, y = I, group = sample), color = "red", alpha = 0.1) + geom_line(data = aggr_df_t_nt, aes (x = dates, y = I_med), color = "red") +  scale_x_date(labels = date_format("%b"), breaks = date_breaks("month")) + xlab('Date') + ylab ('Infections')
Iplot

Isymdetplot<-ggplot() + geom_line(data = df_t_sims , aes(x = dates, y = Isymdet, group = sample), color = "blue", alpha = 0.1) + 
  geom_line(data = aggr_df_t , aes(x = dates, y = Isymdet_med), color = "blue")  +
  geom_line(data = df_t_sims_nt, aes(x = dates, y = Isymdet, group = sample), color = "black", alpha = 0.1) + 
  geom_line(data = aggr_df_t_nt, aes (x = dates, y = Isymdet_med), color = "black") +
  geom_hline(yintercept = N*50/100000, linetype = "dashed", color = "orange") +
  geom_hline(yintercept = N*10/100000, linetype = "dashed", color = "yellow") +
  geom_hline(yintercept = N*100/100000, linetype = "dashed", color = "red") +
  geom_hline(yintercept = N*42/30000, linetype = "dashed", color = "purple") +  scale_x_date(labels = date_format("%b"), breaks = date_breaks("month")) + xlab('Date') + ylab ('Symptomatic detected infections') + coord_cartesian(ylim = c(0,75))
Isymdetplot
```
Vary vaccine coverage, and within each vaccine coverage, simulate different testing frequencies for unvaccinated population. For each vaccine coverage and potentially disease prevalence, find the minimal amount of testing that prevents the university from having to move classes online.
```{r}
# Scenario 1: immunity long-lasting, vaccines remain effective, no major variants
cost_table<-read.csv(COST_TABLE_PATH)
par_table<-read.csv(PAR_TABLE_PATH)
par_table$R0 = 5
par_bounds$R0vals = c(4.5, 5.5)
nsamps<-10# for now set to 10 ( make this 100 for final results)
par_table$w_u<-0.5 # assume 50% of unvaccinated are willing to participate
par_table$f_v<-0 # assume vaccinated don't have to be tested at all
risk_tolerance = 'UT Jan 2021'
vacc_coverage<-seq(from = 0.4, to = 0.8, by = 0.1)
#vacc_coverage<-seq(from = 0.45, to = 0.7, by = 0.05)
#vacc_coverage<-seq(from = 0.5, to = 0.7, by = 0.1)
test_freqs<-c(0, 1/30, 1/14, 1/7, 2/7, 3/7, 1)
test_policies<-c('symptomatic only', 'every month', 'every 2 weeks', 'weekly', '2 times per week', '3 times per week', 'daily')
vacc_policy<-c('40% vaccinated', '50% vaccinated', '60% vaccinated', '70% vaccinated', '80% vaccinated')
pct_per_week_uv_tested<-test_freqs*7*par_table$w_u
N<-par_table$N
#n_tests_per_week_uv<-(1-vacc_coverage)*par_table$N*pct_per_week_uv_tested

# if Scenario 2: immunity from infection wanes, vaccines have reduced efficacy, and new variant is more transmissible
#par_table$e_v<-0.75
#par_table$sigma_v<-0.5
#par_table$alpha_i<-1/180
#par_table$R0 <- 5
#par_table$f_v<-1/7
if (risk_tolerance =='CDC yellow' ){
    close_thres = 10/100000
  }
  if (risk_tolerance == 'CDC orange'){
    close_thres = 50/100000
  }
  if (risk_tolerance == 'CDC red'){
    close_thres = 100/100000
  }
  if (risk_tolerance == 'UT Jan 2021'){
    close_thres = (20 + 0.7*32)/30000 # week ending on 1/16 --> forced school remote in Jan
  }
tdays<-seq(from = 0, to = par_table$duration_school_year)
dates<-seq(from = as.Date("2021-08-20"), by = "day", length.out = par_table$duration_school_year+1)
for(j in 1:length(vacc_coverage)){
    pct_vacc<-vacc_coverage[j]
    par_table$init_vacc<-vacc_coverage[j]
    vacc_cov<-rep(vacc_coverage[j], par_table$duration_school_year+1)
    vacc_policies<-rep(vacc_policy[j], par_table$duration_school_year+1)
    vacc_rate<-vacc_policy[j]
    for (k in 1:length(test_freqs)){
      testing_freq<-test_freqs[k]
      testing_policy<-test_policies[k]
      par_table$f_u<-test_freqs[k]
      test_freq<-rep(test_freqs[k], par_table$duration_school_year+1)
      test_policy<-rep(test_policies[k], par_table$duration_school_year+1)
      testing_policy<-test_policies[k]
      #out_df<-solve_transmission_eqns(par_table)
      #summary_df<-testing_model(par_table, cost_table, risk_tolerance)
      # Get the outputs from each sample and the aggregate outputs over time and in summary
      out_list_uq<-testing_model_w_uncertainty(par_table, cost_table, risk_tolerance,
                                               nsamps, par_bounds)
      df_sim<-out_list_uq[[1]] # contains final results for all nsims
      df_t_sim<-out_list_uq[[2]] # contains time course of results for all nsims
      aggr_df<-out_list_uq[[3]] # contains lb, ub, median of final results 
      aggr_df<-cbind(aggr_df,testing_policy, vacc_rate)
      aggr_df_t<-out_list_uq[[4]] # contains time course of lb, ub, median of results
      aggr_df_t<-cbind(aggr_df_t, test_policy, vacc_policies)
      # check if Isymdet is above each threshold
      above_yellow<-any(aggr_df_t$Isymdet_ub>N*10/100000)
      above_orange<-any(aggr_df_t$Isymdet_ub>N*50/100000)
      above_red<-any(aggr_df_t$Isymdet_ub>N*100/100000)
      above_UT_Jan<-any(aggr_df_t$Isymdet_ub>N*(20 + 0.7*32)/30000)
      # add column indicating whether that testing freq/vaccine coverage combo has an
      # upper bound above the threshold. 
      aggr_df<-cbind(aggr_df, above_yellow, above_orange, above_red, above_UT_Jan)
    
      
      if(k ==1 & j==1){
        df<-df_sim
        df_t<-df_t_sim
        df_uq<-aggr_df
        df_t_uq<-aggr_df_t
    
      }
      else{
        df<-rbind(df, df_sim)
        df_t<-rbind(df_t, df_t_sim)
        df_uq<-rbind(df_uq, aggr_df)
        df_t_uq<-rbind(df_t_uq, aggr_df_t)
      }
      
    }
  }

```
For each vaccine coverage, find the minimum testing needed at each risk tolerance level
```{r}
threshold_prob = 0.05
df_small<-df_uq%>%select(pct_vacc_med, testing_freq_med, days_of_online_med, days_of_online_ub,
                         cross_orange_prob, cross_red_prob, cross_UTJan_prob)
df_min<-get_min_testing_per_vacc(df_uq,threshold_prob, vacc_coverage)
df_min$testing_policy<-factor(df_min$testing_policy, ordered = TRUE,
                         stringr::str_wrap(c("symptomatic only", "every month", "every 2 weeks", "weekly", "2 times per week", "3 times per week", "daily")))
                           
                           #"symptomatic only","every month", 
                                       #"every 2 weeks", "weekly", "2 times per week", "3 times per week", #"daily")))
write.csv(df_uq,'../out/summary_results.csv',row.names = FALSE )
write.csv(df_t_uq, '../out/results_t.csv', row.names = FALSE)
write.csv(df_min, '../out/min_testing.csv', row.names = FALSE)
```
Load in the data frames if don't want to rerun, make smaller dataframe for the main tables

```{r}
close_thres = (20 + 0.7*32)/30000
df_uq<-read.csv('../out/summary_results.csv')
df_t_uq<-read.csv('../out/results_t.csv')
df_min<-read.csv('../out/min_testing.csv')
df_print<-df_uq%>%select(pct_vacc_med,testing_policy, n_inf_med, n_inf_lb, n_inf_ub, max_symdet_med, max_symdet_lb, max_symdet_ub)

df_t_uq$test_policy<-factor(df_t_uq$test_policy, ordered = TRUE,
                         stringr::str_wrap(c("daily", "3 times per week",
                                             "2 times per week", 
                                       "weekly", "every 2 weeks", "every month", 
                                       "symptomatic only")))

path = "../out/sym_det_t_all.png"
# First plot testing needed
thres_sym_det<-ggplot(df_t_uq) + geom_line(aes(x = as.Date(dates), y = Isymdet_med, group = factor(test_policy), color = factor(test_policy))) + geom_ribbon(aes(x = as.Date(dates), ymin = Isymdet_lb, ymax = Isymdet_ub, group = factor(test_policy), fill = factor(test_policy)), alpha = 0.1)+ geom_hline(yintercept = N*100/100000, color = "gray")+ facet_grid(~vacc_policies)+geom_hline(yintercept = N*(20 + 0.7*32)/30000, color = "gray48") + labs(color = "Test frequency") + xlab('Date') + ylab('Symptomatic Detected Cases')  + scale_color_brewer(palette = "Set2", direction = -1) +scale_fill_brewer(palette = "Set2", direction = -1) + coord_cartesian(ylim = c(0,6*N*close_thres )) +
  theme(axis.text.x = element_text(angle=45, hjust = 1)) + theme(legend.position = "none", legend.text= element_text(size = 12)) +  scale_x_date(date_labels = "%b") + guides(fill = FALSE) 
thres_sym_det
ggsave(filename = path, device = "png", dpi = 700)

path = "../out/sym_det_t.png"
# First plot testing needed
df_t_uq_sel<-df_t_uq%>%filter(pct_vacc_med ==0.6 | pct_vacc_med == 0.8)
thres_sym_det_sel<-ggplot(df_t_uq_sel) + geom_line(aes(x = as.Date(dates), y = Isymdet_med, group = factor(test_policy), color = factor(test_policy))) + geom_ribbon(aes(x = as.Date(dates), ymin = Isymdet_lb, ymax = Isymdet_ub, group = factor(test_policy), fill = factor(test_policy)), alpha = 0.1)+ geom_hline(yintercept = N*100/100000, color = "gray", alpha = 0.5)+ facet_grid(~vacc_policies)+geom_hline(yintercept = N*(20 + 0.7*32)/30000, color = "gray48") + labs(color = "Test frequency") + xlab('Date') + ylab('Symptomatic Detected Cases')  + scale_color_brewer(palette = "Set2", direction = -1) +scale_fill_brewer(palette = "Set2", direction = -1) + coord_cartesian(ylim = c(0,2*N*close_thres )) +
  theme(axis.text.x = element_text(angle=45, hjust = 1)) + theme(aspect.ratio = 1, legend.position = "right", legend.text= element_text(size = 11)) +  scale_x_date(date_labels = "%b") + guides(fill = FALSE) 
thres_sym_det_sel
ggsave(filename = path, device = "png", dpi = 700)
```
Plot and report the minimum amount of testing needed at each vaccination level and risk tolerance
```{r}
df_UTJan<-df_min%>%filter(thres == "UT Jan")
path = '../out/test_freq.png'
bar_test_freq<-ggplot(df_UTJan, aes(x = 100*pct_vacc_med, y = 7*testing_freq_med)) + geom_bar(stat = "identity", position = position_dodge())  + xlab('Percent vaccinated') + ylab('Recommended frequency (tests per week)') + guides(fill = FALSE)+theme(aspect.ratio = 1, axis.title.y = element_text(size =14))
bar_test_freq
ggsave(filename = path, device = "png", dpi = 700)
path = '../out/tot_tests.png'
bar_tot_tests<-ggplot(df_UTJan, aes(x = 100*pct_vacc_med, y = n_tests_per_week_med)) + geom_bar(stat = "identity", position = position_dodge()) + xlab('Percent vaccinated') + ylab('Total tests per week')+guides(fill = FALSE) + theme(aspect.ratio = 1)
bar_tot_tests
ggsave(filename = path, device = "png", dpi = 700)
path = '../out/fig2.png'

# Concise table for including in report
df_table_tests<-df_UTJan%>%select(pct_vacc_med, n_tests_per_week_med, testing_policy)
```
Make cost breakdown figures for all levels of testing
```{r}
df_long<-df_uq%>%
  dplyr::select(pct_vacc_med, vacc_rate, testing_freq_med, testing_policy, n_kiosks_med, 
                              pct_inf_med, cost_PCR_med,
                              cost_RT_med, cost_isofac_med, cost_sequencing_med, cost_kiosks_med,
                              cost_contact_tracing_med, cost_of_online_med)%>%
  pivot_longer(cols = starts_with("cost_"),names_to = "Source",names_prefix = "cost_", values_to = "cost" )%>%mutate(test_strategy = 'yes')
df_long$testing_policy<-factor(df_long$testing_policy, ordered = TRUE,
                         stringr::str_wrap(c("symptomatic only","every month", 
                                       "every 2 weeks", "weekly", "2 times per week", "3 times per week",
                                       "daily")))
df_uq$testing_policy<-factor(df_uq$testing_policy, ordered = TRUE,
                         stringr::str_wrap(c("symptomatic only","every month", 
                                       "every 2 weeks", "weekly", "2 times per week", "3 times per week",
                                       "daily")))


df_long$Source<-factor(df_long$Source, ordered = TRUE,
                         stringr::str_wrap(c("of_online_med", "contact_tracing_med",
                                             "isofac_med", 
                                       "kiosks_med", "PCR_med", "RT_med", 
                                       "sequencing_med")))
path = "../out/figA3_costs.png"
bar_costs_comb<-ggplot(df_long, aes (x = testing_policy, y = cost/1e6, fill = factor(Source))) + geom_bar(stat = "identity", position = "stack") + facet_wrap(~vacc_rate, ncol = 6) +  scale_fill_brewer(palette = "Set1", direction = -1)+
xlab('Test Frequency') + ylab('Cost to UT (millions)') +labs(fill = "Source of cost") + theme(legend.position = "none", legend.text = element_blank(), legend.title = element_blank(), axis.text.y = element_text(size = 8), axis.title = element_text(size = 12)) + theme(axis.text.x = element_text(angle=45, hjust = 1, size = 8), aspect.ratio =1.3) 
bar_costs_comb
ggsave(filename = path, device = "png", dpi = 700)


path = "../out/figA3_inf.png"
bar_inf<-ggplot(df_uq, aes(x = testing_policy, y = n_inf_med/1000)) + geom_bar(stat = "identity", position = "stack") + facet_wrap(~vacc_rate, ncol = 6) + geom_errorbar(aes(ymin = n_inf_lb/1000, ymax= n_inf_ub/1000), width = 0.1, position = position_dodge(0.04)) + xlab('Test frequency') + ylab('Infections (thousands)')  + theme(axis.text.x = element_blank(), axis.title.x = element_blank(), axis.title = element_text(size = 12), legend.position = "none", aspect.ratio =1.3)+ scale_fill_gradient(low = "blue", high = "red")
bar_inf
ggsave(filename = path, device = "png", dpi = 700)

# Do only for 60% and 80% vaccination

# Make the figure with only 50 and 80% vaccination 
path = "../out/fig2a.png"
df_long_sel<-df_long%>%filter(pct_vacc_med==0.6 | pct_vacc_med == 0.8)
bar_costs_comb_sel<-ggplot(df_long_sel, aes (x = testing_policy, y = cost/1e6, fill = factor(Source))) + geom_bar(stat = "identity", position = "stack") + facet_wrap(~vacc_rate, ncol = 6) +  scale_fill_brewer(palette = "Set1", direction = -1) + xlab('Test Frequency') + ylab('Cost to UT (millions)') +labs(fill = "Source of cost") + theme(legend.position = "none", legend.text = element_blank(), legend.title = element_blank(), axis.text.y = element_text(size = 10), axis.title = element_text(size = 14)) + theme(axis.text.x = element_text(angle=45, hjust = 1, size = 11.5)) 
bar_costs_comb_sel
ggsave(filename = path, device = "png", dpi = 700)

path = "../out/fig2b.png"
df_uq_sel<-df_uq%>%filter(pct_vacc_med== 0.6 |pct_vacc_med == 0.8)
bar_inf_sel<-ggplot(df_uq_sel, aes(x = testing_policy, y = n_inf_med/1000)) + geom_bar(stat = "identity", position = "stack") + facet_wrap(~vacc_rate, ncol = 6) + geom_errorbar(aes(ymin = n_inf_lb/1000, ymax= n_inf_ub/1000), width = 0.1, position = position_dodge(0.04))  + ylab('Infections (thousands)')  + theme(axis.text.x = element_blank(),axis.title = element_text(size = 14), legend.position = "none")+ scale_fill_gradient(low = "blue", high = "red")
bar_inf_sel
ggsave(filename = path, device = "png", dpi = 700)

```
Housing projections
```{r}
nsamps<-100
cost_table<-read.csv(COST_TABLE_PATH)
par_table<-read.csv(PAR_TABLE_PATH)
par_bounds<-read.csv(PAR_BOUNDS_PATH)
par_table$intros_per_week<-5
par_bounds$intro_vals<-c(2, 8)
par_table$init_rec<-0.35
par_bounds$init_rec_vals<-c(0.27, 0.43) # using updated estimates
par_table$N<-7400
iso_prob<-0.8
par_table$f_v<-0 # assume vaccinated don't have to be tested at all
par_table$f_u<-0
vacc_coverage<-seq(from = 0.4, to = 0.8, by = 0.1)


tdays<-seq(from = 0, to = par_table$duration_school_year)
dates<-seq(from = as.Date("2021-08-20"), by = "day", length.out = par_table$duration_school_year+1)
for(j in 1:length(vacc_coverage)){
    pct_vacc<-vacc_coverage[j]
    par_table$init_vacc<-vacc_coverage[j]
    vacc_cov<-rep(vacc_coverage[j], par_table$duration_school_year+1)
    out_list_uq<-testing_model_w_uncertainty(par_table, cost_table, risk_tolerance, nsamps,
                                             par_bounds)
  aggr_df_t<-out_list_uq[[4]]
  aggr_df<-out_list_uq[[3]]
  df_t_sims<-out_list_uq[[2]]
  df_sims<-out_list_uq[[1]]
      # time dependent variables
      # all those in aggr_df_t
      isofac_t_med<-aggr_df_t$Isymdet_med*iso_prob
      isofac_t_lb<-aggr_df_t$Isymdet_lb*iso_prob
      isofac_t_ub<-aggr_df_t$Isymdet_ub*iso_prob
      isofac_10d<-rollmean(isofac_t_med, k=7, fill =NA) # Find 10 day rolling average of isofac_t
      # static variables
      n_isofac_med<-iso_prob*aggr_df$n_pos_med
      n_isofac_lb<-iso_prob*aggr_df$n_pos_lb
      n_isofac_ub<-iso_prob*aggr_df$n_pos_ub
      max_isofac_med<-max(isofac_t_med)
      imed<-which.max(isofac_t_med)
      date_max<-dates[imed]
      max_isofac_lb<-max(isofac_t_lb)
      max_isofac_ub<-max(isofac_t_ub)
    if(j==1 ){
        df_t<-cbind(aggr_df_t, vacc_cov, isofac_t_med, isofac_t_lb, isofac_t_ub,
                    isofac_10d)
        df<-cbind(aggr_df, n_isofac_med, n_isofac_lb, n_isofac_ub, max_isofac_med, 
                  max_isofac_lb, max_isofac_ub,date_max, pct_vacc)
      }
      else{
        df_ti<-cbind(aggr_df_t, vacc_cov, isofac_t_med, isofac_t_lb, isofac_t_ub,
                     isofac_10d)
        dfi<-cbind(aggr_df, n_isofac_med, n_isofac_lb, n_isofac_ub, max_isofac_med, 
                  max_isofac_lb, max_isofac_ub, date_max, pct_vacc)
        df_t<-rbind(df_t, df_ti)
        df<-rbind(df, dfi)
      }
      
}

write.csv(df_t, '../out/df_t_housing.csv')
write.csv(df, '../out/df_housing.csv')

#df<-read.csv('../out/df_housing.csv')
#df_t<-read.csv('../out/df_t_housing.csv')
df_isofac_table<-df%>%select(pct_vacc_med, date_max, max_isofac_med, max_isofac_lb, max_isofac_ub, n_isofac_med, n_isofac_lb, n_isofac_ub, n_inf_med, n_inf_lb, n_inf_ub)
path = "../out/isofac_t.png"
# Plot isofac usage over time as a function of vaccine coverage
isofac_use<-ggplot(df_t) + geom_line(aes(x = dates, y = isofac_t_med, 
   color = factor(vacc_cov))) + geom_ribbon(aes(x = dates, ymin = isofac_t_lb, 
  ymax = isofac_t_ub, fill = factor(vacc_cov)), alpha = 0.1) + 
  xlab('Date') + ylab('Students in isolation facility')  + scale_color_brewer(palette = "Spectral", direction = -1) + scale_fill_brewer(palette = "Spectral", direction = -1)+theme(legend.position = "none") + guides(fill = FALSE)
isofac_use
ggsave(filename = path, device = "png", dpi = 700)

path = "../out/isofac_max.png"
isofac_max<-ggplot(df, aes(x = 100*pct_vacc, y = max_isofac_med, fill = factor(100*pct_vacc))) + 
  geom_bar(stat = "identity")+geom_errorbar(aes(ymin = max_isofac_lb, ymax= max_isofac_ub), width = 0.01, position = position_dodge(0.04)) + scale_fill_brewer(palette = "Spectral", direction = -1) + xlab('Percent vaccinated') + ylab('Peak occupancy') +labs(fill = 'Percent vaccinated')
isofac_max
ggsave(filename = path, device = "png", dpi = 700)
```

Sensitivity analysis on the likelihood/overlap between unvaccinated and those previously infected
```{r}
cost_table<-read.csv(COST_TABLE_PATH)
par_table<-read.csv(PAR_TABLE_PATH)
par_bounds<-read.csv(PAR_BOUNDS_PATH)
odds_inf_not_vac_vec<-seq(from = 0.5, to = 3, by = 0.5)
pct_vacc_vec<-seq(from = 0.4, to = 0.8, by = 0.1)
par_table$f_u<-0
vacc_policy<-c('40% vaccinated', '50% vaccinated', '60% vaccinated', '70% vaccinated', '80% vaccinated')

N<-par_table$N
tdays<-seq(from = 0, to = par_table$duration_school_year)
dates<-seq(from = as.Date("2021-08-20"), by = "day", length.out = par_table$duration_school_year+1)
for(j in 1:length(pct_vacc_vec)){
    par_table$init_vacc<-pct_vacc_vec[j]
    vacc_policies<-rep(vacc_policy[j], par_table$duration_school_year+1)
    for (k in 1:length(odds_inf_not_vac_vec)){
      par_table$odds_inf_not_vac<-odds_inf_not_vac_vec[k]
      odds_prev_inf<-rep(odds_inf_not_vac_vec[k],  par_table$duration_school_year +1)
      out_list_uq<-testing_model_w_uncertainty(par_table, cost_table, risk_tolerance,
                                               nsamps, par_bounds, vacc_inf_correlation = 'correlated')
      df_sim<-out_list_uq[[1]]
      df_t_sim<-out_list_uq[[2]]
      aggr_df<-out_list_uq[[3]]
      aggr_df_t<-out_list_uq[[4]]
      aggr_df_t<-cbind(aggr_df_t, vacc_policies, odds_prev_inf)
      if(k ==1 & j==1){
        df<-df_sim
        df_t<-df_t_sim
        df_uq<-aggr_df
        df_t_uq<-aggr_df_t
    
      }
      else{
        df<-rbind(df, df_sim)
        df_t<-rbind(df_t, df_t_sim)
        df_uq<-rbind(df_uq, aggr_df)
        df_t_uq<-rbind(df_t_uq, aggr_df_t)
      }
      
    }
}

N = 50000
path = "../out/sens_analysis_vac_corr.png"
# First plot testing needed
sensitivity_to_vacc<-ggplot(df_t_uq) + geom_line(aes(x = as.Date(dates), y = Isymdet_med, group = factor(odds_prev_inf), color = factor(odds_prev_inf))) + geom_ribbon(aes(x = as.Date(dates), ymin = Isymdet_lb, ymax = Isymdet_ub, group = factor(odds_prev_inf), fill = factor(odds_prev_inf)), alpha = 0.1)+ geom_hline(yintercept = N*close_thres, color = "gray48") + geom_hline(yintercept = N*100/100000, color = "gray")+ facet_grid(~vacc_policies) + labs(color = "Odds previously infected in unvaccinated") + xlab('Date') + ylab('Symptomatic Detected Cases')  + scale_color_brewer(palette = "BrBG", direction = -1) +scale_fill_brewer(palette = "BrBG", direction = -1) + coord_cartesian(ylim = c(0,4*N*close_thres )) +
  theme(axis.text.x = element_text(angle=45, hjust = 1)) + theme(legend.position = "bottom", legend.text= element_text(size = 12)) +  scale_x_date(date_labels = "%b") + guides(fill = FALSE) + labs(color = "Odds previously infected if unvaccinated")
sensitivity_to_vacc
ggsave(filename = path, device = "png", dpi = 700)
