---
title: "UT_vaccine_coverage_estimates"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(lubridate)
```
Load in county-level vaccine data 
```{r}
rm(list=ls())
student_origin= read.csv('../data/student_geo_codes_2021_07_26.csv')
#vacc_by_county = read.csv('../data/vaccine_coverage18to24_TX_6_21.csv')
# Vaccine data
vacc_by_age_county_tx = read.csv('../data/county_vaccinations_age_date_2021-07-26.csv') # texas
vacc_by_county_US = read.csv('../data/COVID-19_Vaccinations_in_the_United_States_County.csv') # US

# Zip to county from: https://simplemaps.com/data/us-zips
zip_to_county<-read.csv('../data/uszips.csv')%>%
  select(zip, county_fips, county_name)


BINOM_SAMPS<-100
```
Summarise line-list student data into students per county
```{r}


# Assume that if student has permanent state in Texas, then TX vaccination/case data
# is relevant. 
student_origin_tx<-student_origin%>%filter(ORI_GEOG_CODE>0 & ORI_GEOG_CODE<300) # 40061 students have permanent in texas
student_origin_tx['zip']<-as.numeric(gsub("(^\\d{5}).*", "\\1", student_origin_tx$PERM_ZIP))
student_origin_tx<-student_origin_tx%>%mutate(county = ORI_GEOG_NAME)

student_origin_not_tx<-student_origin%>%filter(ORI_GEOG_CODE>=300) 
# US not TX
student_origin_us<-student_origin_not_tx%>%filter(ORI_GEOG_CODE>=300 &ORI_GEOG_CODE<=370) #3878us not texas not foreign
student_origin_us['zip']<-as.numeric(gsub("(^\\d{5}).*", "\\1", student_origin_us$PERM_ZIP))
student_origin_us<-student_origin_us%>%left_join(zip_to_county, by = "zip")%>%
  mutate(county = county_name,
         county_fips = as.character(county_fips))


# non-US
student_origin_foreign<-student_origin_not_tx%>%filter(ORI_GEOG_CODE>=400)
student_origin_foreign<-student_origin_foreign%>%mutate(county = "foreign", county_fips = NA)#1534 foreign

# TX
students_by_county_tx<-student_origin_tx%>%
  group_by(county)%>%
  summarise(n_students = n())
#US not TX
students_by_county_us<-student_origin_us%>%
  group_by(county_fips)%>%
  summarise(n_students = n())
# foreign
students_foreign<-student_origin_foreign%>%
  group_by(county)%>%
  summarise(n_students = n())

```

Filter the vaccination data sets to get most recent data and most relevant age 
```{r}
# TX county and proportions as of 7-26-2021
vacc_by_county_tx<-vacc_by_age_county_tx%>%filter(date <= as.Date("2021-07-25"), 
                                                  date >= as.Date("2021-06-25"),
                                                  age_group == "16-49 years")%>%
  mutate(prop_first_dose = one_dose/population,
         prop_fully_vax = fully_vax/population)%>%
  select(date, county, tsa_name, prop_first_dose, prop_fully_vax)
# US counties county and proportions as of 7-25-2021
vacc_by_county_US<-vacc_by_county_US%>%mutate(date = mdy(Date))%>%
  filter(date <= as.Date("2021-07-25"), 
         date >= as.Date("2021-06-25"))%>%
  mutate(prop_first_dose =Administered_Dose1_Recip_18PlusPop_Pct/100,
         prop_fully_vax = Series_Complete_18PlusPop_Pct/100,
         county = Recip_County,
         county_fips = as.character(FIPS),
         state = Recip_State,
         tsa_name = NA)%>%
  arrange(date)%>%
  filter(state!='TX')%>%
  select(date, state, county, county_fips, tsa_name, prop_first_dose, prop_fully_vax)# use the 18+ percent? might be an overestimate 

vacc_by_county_US$county<-gsub("County", "", as.character(vacc_by_county_US$county))
```
Use the vaccination data set timecourses to estimate prop_fully_vax_pred
```{r}
# First do this for TX data
TX_counties<-vacc_by_county_tx$county%>%unique()
for (i in 1:length(TX_counties)){
  county_df<-vacc_by_county_tx%>%filter(county == TX_counties[i])
  county_df$t<-yday(county_df$date)-yday(county_df$date[1])
  county_df$t_pred<-seq(from = nrow(county_df), to = 2*nrow(county_df)-1, by = 1)
  county_df$date_pred<-seq(from = as.Date("2021-07-26"), to = as.Date("2021-08-25"), by = 'days')
  # Fit a linear model to t vs prop_fully_vacc
  fit<-lm(prop_fully_vax ~t, data = county_df)
  betas<-coefficients(fit)
  county_df$fit<-betas[1] + betas[2]*county_df$t
  county_df$prop_fully_vax_pred = betas[1] + betas[2]*county_df$t_pred
  county_df$daily_rate_of_vax<-betas[2]
  
  if(i==1){
    vacc_by_county_tx_t<-county_df
  }
  else{
    vacc_by_county_tx_t<-rbind(vacc_by_county_tx_t, county_df)
  }
}
vacc_by_county_tx_pred<-vacc_by_county_tx_t%>%filter(date == as.Date("2021-07-25"))


test<-ggplot(data = county_df) + geom_point(aes(x = as.Date(date), y = prop_fully_vax)) + 
  geom_line(aes(x = as.Date(date), y = fit))+
  geom_line(aes(x = as.Date(date_pred), y = prop_fully_vax_pred), color = "red") + xlab('Date') +
  ylab('Proportion fully vaccinated') + ggtitle(paste(as.character(county_df$county), 'COUNTY'))
test

all_counties_tx<-ggplot(data = vacc_by_county_tx_t) + geom_point(aes(x = as.Date(date), y = prop_fully_vax, group = county, color= county)) + 
  geom_line(aes(x = as.Date(date), y = fit, group = county, color = county))+
  geom_line(aes(x = as.Date(date_pred), y = prop_fully_vax_pred, group = county, color = county), linetype = "dashed") + xlab('Date') + theme(legend.position = "none")+
  ylab('Proportion fully vaccinated') + ggtitle('Projected rates by county in TX')
all_counties_tx
```
```{r}
# Now do this for the US
US_counties<-vacc_by_county_US$county_fips%>%unique()
for (i in 1:length(US_counties)){
  county_df<-vacc_by_county_US%>%filter(county_fips == US_counties[i])
  county_df$t<-yday(county_df$date)-yday(as.Date("2021-06-25")) # in case not all dates available
  # Fit a linear model to t vs prop_fully_vacc
  fit<-lm(prop_fully_vax ~t, data = county_df)
  betas<-coefficients(fit)
  county_df$fit<-betas[1] + betas[2]*county_df$t
  
  # Make a new future df
  date_pred<- seq(from = as.Date("2021-07-26"), to = as.Date("2021-08-25"), by = 'days')
  t_pred<-yday(date_pred)-yday(as.Date("2021-06-25"))
  prop_fully_vax_pred <- betas[1] + betas[2]*t_pred
  prop_fully_vax_pred[prop_fully_vax_pred>1]<-1 # set max to 1
  county_df_pred<-data.frame(date_pred, t_pred, prop_fully_vax_pred)
  county_df_pred$county_fips<-rep(US_counties[i],)
  county_df_pred$county<-rep(county_df$county[1],)
  
  if(i==1){
    vacc_by_county_us_t_fit<-county_df
    vacc_by_county_us_t_pred<-county_df_pred
  }
  else{
    vacc_by_county_us_t_fit<-rbind(vacc_by_county_us_t_fit, county_df)
    vacc_by_county_us_t_pred<-rbind(vacc_by_county_us_t_pred, county_df_pred)
  }
}
```
```{r}
vacc_by_county_us_curr<-vacc_by_county_us_t_fit%>%filter(date == as.Date("2021-07-25"))
vacc_by_county_us_pred<-vacc_by_county_us_t_pred%>%filter(date_pred == as.Date("2021-08-25"))
max_fully_vax<-which.max(vacc_by_county_us_curr$prop_fully_vax)
max_county<-vacc_by_county_us_curr[max_fully_vax,]

test<-ggplot() + geom_point(data = county_df, aes(x = as.Date(date), y = prop_fully_vax)) + 
  geom_line(data = county_df, aes(x = as.Date(date), y = fit))+
  geom_line(data = county_df_pred, aes(x = as.Date(date_pred), y = prop_fully_vax_pred), color = "red") + xlab('Date') +
  ylab('Proportion fully vaccinated') + ggtitle(paste(as.character(county_df$county)))
test


vacc_by_county_us_t_pred_small<-vacc_by_county_us_t_pred[1:1000, ]

all_counties<-ggplot() + geom_line(data = vacc_by_county_us_t_pred, aes(x = as.Date(date_pred), y = prop_fully_vax_pred, group = county_fips, color= county), linetype = "dashed") + geom_line(data = vacc_by_county_us_t_fit, aes(x = as.Date(date), y = fit, group = county_fips, color = county))+
  geom_point(data = vacc_by_county_us_t_fit, aes(x = as.Date(date), y = prop_fully_vax, group = county_fips, color = county))+ xlab('Date') + theme(legend.position = "none")+
  ylab('Proportion fully vaccinated') + ggtitle('Projected rates by county in US')
all_counties

# Confirm that no counties where students are coming from have estimates that would be above 1
false_ones_us<-vacc_by_county_us_curr%>%filter(prop_fully_vax ==1)
false_ones_us<-false_ones_us%>%inner_join(students_by_county_us, by = "county_fips")%>%distinct()
``` 




```{r}
# Check for missing data 
false_zeros_tx<-vacc_by_county_tx_pred%>%filter(prop_fully_vax_pred ==0)
false_zeros_US<-vacc_by_county_us_pred%>%filter(prop_fully_vax_pred ==0)
false_zeros_US<-false_zeros_US%>%inner_join(students_by_county_us, by = "county_fips")%>%distinct()
# 10 students from places with erroneous 0s. We will exclude these from the prevalence estimate. 
exclude_fips<-false_zeros_US$county_fips
students_by_county_us<-students_by_county_us%>%filter(county_fips!= exclude_fips)
```




Combine vaccination data and number of students per county data
```{r}

# Join with the vaccination data by county or county ID in the non-TX US
# TX
student_vacc_tx<-vacc_by_county_tx_pred%>%left_join(students_by_county_tx, by = "county")
student_vacc_tx_counties<-student_vacc_tx
student_vacc_tx<-student_vacc_tx%>%select(n_students, prop_fully_vax_pred)
# US not TX
student_vacc_us<-students_by_county_us%>%left_join(vacc_by_county_us_pred, by = "county_fips")
# Assume the unknown counties are Travis ? Or can also use the nationwide average
#ATX_first_dose_val<-vacc_by_county_tx$prop_first_dose[vacc_by_county_tx$county=="TRAVIS"]
ATX_fully_vax_val<-vacc_by_county_tx_pred$prop_fully_vax_pred[vacc_by_county_tx_pred$county=="TRAVIS"]
#student_vacc_us$prop_first_dose[is.na(student_vacc_us$prop_first_dose)] <-ATX_first_dose_val
student_vacc_us$prop_fully_vax_pred[is.na(student_vacc_us$prop_fully_vax_pred)] <-ATX_fully_vax_val
student_vacc_us<-student_vacc_us%>%select(n_students, prop_fully_vax_pred)
student_vacc_foreign<-students_foreign%>%mutate(prop_fully_vax_pred= ATX_fully_vax_val)%>%
        select(n_students, prop_fully_vax_pred)


student_vacc<-rbind(student_vacc_tx, student_vacc_us)
student_vacc<-rbind(student_vacc, student_vacc_foreign)
student_vacc<-student_vacc%>%drop_na(n_students)

```
Use students per county and vaccination rate in county to estimate overall vaccination rate. 
```{r}
#vacc_first_dose_mat<-matrix(nrow = nrow(student_vacc), ncol = BINOM_SAMPS)
vacc_full_mat<-matrix(nrow = nrow(student_vacc), ncol = BINOM_SAMPS)

for (j in 1:nrow(student_vacc)){
    # sample the number of vaccinated students from that county:
    #vacc_first_dose_mat[j,]<-rbinom(BINOM_SAMPS,size = student_vacc$n_students[j], prob = student_vacc$prop_first_dose[j])
    vacc_full_mat[j,]<-rbinom(BINOM_SAMPS,size = student_vacc$n_students[j], prob = student_vacc$prop_fully_vax_pred[j])
}

total_students<-sum(student_vacc$n_students)
#first_dose_distrib<-colSums(vacc_first_dose_mat, na.rm = TRUE)
fully_vacc_distrib<-colSums(vacc_full_mat, na.rm = TRUE)
#first_dose_CI<-first_dose_distrib%>%quantile(probs = c(0.025, 0.5, 0.975), na.rm = TRUE)
#pct_first_dose_CI<-100*first_dose_CI/total_students
fully_vacc_CI<-fully_vacc_distrib%>%quantile(probs = c(0.025, 0.5, 0.975), na.rm = TRUE)
pct_fully_vacc_CI<-100*fully_vacc_CI/total_students
print(pct_fully_vacc_CI)
#print(pct_first_dose_CI)

age_odds = 28.4/35.5 #https://www.cdc.gov/mmwr/volumes/70/wr/mm7025e2.htm
college_education_odds = 86/76.4 #https://covid19pulse.usc.edu/
pct_fully_vacc_median = pct_fully_vacc_CI[2]
pct_fully_vacc_lb = pct_fully_vacc_CI[2]*age_odds
pct_fully_vacc_ub = pct_fully_vacc_CI[2]*college_education_odds

pct_fully_vacc_range<-c(pct_fully_vacc_lb, pct_fully_vacc_median, pct_fully_vacc_ub)
print(pct_fully_vacc_range)

student_vacc<-student_vacc[with(student_vacc, order(-n_students)),]
# Add Labels to these counties

```
